**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2021-01-19 paper/manuscript.Rmd
outline results

## Results
- Of the five ML methods tested, Random forest was consistently the top performer (supplemental figure of all models?) at most taxonomic levels.
  - RF might be more appropriate anyways since its more suitable for zero inflated data? (need to look into literature)
- Within the RF model, the highest AUCs were observed for family, genus, and otu level data with no significant difference between the three. (Figure 1)

>>>>

## Results
- Across the five ML methods tested, model performance tends to increase with taxnomic level usually peaking around genus level and dropping off slightly with ASVs.
- Random forest was consistently the top performer at most taxonomic levels.
  - RF might be more appropriate for microbiome analysis since its more suitable for zero inflated data (need to look into literature)
- Within the RF model, the highest AUCs were observed for family, genus, and otu level data with no significant difference between the three (Figure 1). ASV performed significantly lower than OTU but not family and genus levels.

### 2021-01-19 paper/manuscript.tex
outline results

\textbf{(observation format - max 1200 words, 2 figures, 25 ref)}

@@

\begin{itemize}
\tightlist
\item
  Of the five ML methods tested, Random forest was consistently the top
  performer (supplemental figure of all models?) at most taxonomic
  levels.

  \begin{itemize}
  \tightlist
  \item
    RF might be more appropriate anyways since its more suitable for
    zero inflated data? (need to look into literature)
  \end{itemize}
\item
  Within the RF model, the highest AUCs were observed for family, genus,
  and otu level data with no significant difference between the three.
  (Figure 1)
\end{itemize}

>>>>

\textbf{observation format - max 1200 words, 2 figures, 25 ref}

@@

\begin{itemize}
\tightlist
\item
  Across the five ML methods tested, model performance tends to increase
  with taxnomic level usually peaking around genus level and dropping
  off slightly with ASVs.
\item
  Random forest was consistently the top performer at most taxonomic
  levels.

  \begin{itemize}
  \tightlist
  \item
    RF might be more appropriate for microbiome analysis since its more
    suitable for zero inflated data (need to look into literature)
  \end{itemize}
\item
  Within the RF model, the highest AUCs were observed for family, genus,
  and otu level data with no significant difference between the three
  (Figure 1). ASV performed significantly lower than OTU but not family
  and genus levels.
\end{itemize}
